\chapter{
    Macroeconomic Principles
}\label{chap:macroeconomics}

Chapter~\ref{chap:compliance} investigated distributed ledger systems from a
microeconomic perspective, focusing on the incentives and strategic choices of
individual parties. Nonetheless, if such systems are to support real-world
economies, a macroeconomic treatment is also imperative. In this chapter, we
provide some preliminary results on this line of research.

Section~\ref{sec:egalitarianism} explores the limitations in enforcing
macroeconomic policies in distributed ledgers. Importantly, we show that, in
decentralized anonymous systems, no macroeconomic policy which redistributes
wealth from the larger to the smaller parties can be applied. Instead, the best
one can hope for is a linear increase in each party's wealth, proportionally to
their capital. To quantify how different systems fare in this regard, we
introduce the notion of ``cryptocurrency egalitarianism'', a quantitative
metric that helps compare systems \wrt how much they favor wealthy investors.

Next, Section~\ref{sec:taxation} explores how taxation could be enforced. Given
the previous impossibility result, we assume the existence of a centralized
taxation authority. Our goal is to enable the authority to correctly identify
the users' assets, in order to enforce its taxation policy, in a
privacy-preserving and efficient manner. In that direction, we propose two
schemes based on programmable money, \ie currency which is transferable as long
as certain preconditions are met.

\input{content/egalitarianism/main}
\input{content/taxation/main}
