\paragraph{\bf Part 1: Stake Pool Management.}
The pool's management (Figure~\ref{fig:Fpool-1}) includes all operations that
are not consensus-oriented.  First, establishing a stake pool consists of two
parts, defined as corresponding interfaces in the ideal functionality. The
pool's members \emph{gather} and jointly decide to create a staking pool; they
contact each other, \eg via off-chain channels, agree on the pool's parameters,
and generate its key.  Importantly, the participants are aware of the total
number of participants in the pool, as well as their weights. Then, The pool's
members perform a setup protocol and \emph{register} the new pool via a
\emph{registration certificate}, which is signed by the pool's key and
published on the ledger.
% We highlight that each party needs to delegate its stake to the newly created
% pool prior to the establishing of the pool, \ie before it can participate in
% the consensus protocol.\dimitris{is this needed?}
Following, the pool receives rewards for participating in the consensus
protocol. The rewards are managed by a smart contract and, at any point, each
each party can withdraw their part, which is proportional to the internal stake
distribution. Finally, to close the pool, the members sign and publish a
revocation certificate.

\paragraph{\bf Part 2: Participation in Consensus.}
Following registration, participation in the system (Figure~\ref{fig:Fpool-2})
consists of \emph{validating transactions} and \emph{issuing blocks}. To
improve performance, we define a subselection mechanism, which elects a subset
of parties to verify each transaction and (potentially) add it to the
distributed mempool. At any point, all (honest) pool members keep the same view
of the distributed mempool and, when the pool is elected to participate in
consensus, its members locally construct the new block, collectively sign it,
and publish it.

%$\Fpool$ is compatible with the framework of~\cite{SCN:KarKiaLar20}, \ie it
%generates the registration and revocation certificates $\cert_{reg}$ and
%$\cert_{rev}$. The validity of $\cert_{reg}$ requires that, to join the pool,
%each party $\p_{i}$ publishes an individual delegation certificate to the
%(joint) stake pool public key $\threshpubkey_{pool}$, prior to the generation
%of the registration certificate $\cert_{reg}$.\dimitris{is this necessary?}
